### 2015-04-16 usecase-combinatoric.tex
Fix typos.  Add gperftools section.

\subsubsection{Gperftools packaging}
\todo{.5 page}

\begin{verbatim}
	- combinatoric nightmare
	- compilers x versions
\end{verbatim}

>>>>

\subsubsection{Gperftools packaging}

The gperftools tool from Google has gained popularity among some developers for its high-performance thread-safe heap and its lite-weight profilers.  Unfortunately, two issues made it difficult to maintain gperftools installations at LLNL.  First, gperftools is a C++ library.  Since C++ does not have standard ABI it needs to be re-built with each compiler and compiler version.  Second, building gperftools on atypical architectures (such as Blue Gene/Q) requires patches and a complicated configure lines that change with each compiler.  The first issue motivated application developers to try and maintain their own builds of gperftools that worked with their prefered compilers--a task that was made difficult by the second issue.

Spack presented a solution to both problems.  Site administrators can use Spack to easily maintain a central install of gperftools across the combinations of versions and compilers.  Spack's gperftools package also serves as a central repository for the knowledge of how to build gperftools on each platform and compiler combination.

\begin{figure}
  \includegraphics[width=\columnwidth]{code/gperftools.pdf}
  \caption{
    Simplified install routine for the gperftools tool.
    \label{fig:gperftools}
  }
\end{figure}

Figure~\ref{fig:gperftools} illustrates per-compiler and platform build rules with a simplified version of the install routine for the gperftools tool (Spack's real install routine for gperftools includes other compilers and more options per compiler).  It applies a patch if gperftools 2.4 is built with the XLC compiler, and it selects the correct configure line based on the current platform and compiler.
